---
title: "Hausaufgabe 04 - Mehr {dplyr}"
author: "Füge deinen Namen hier hinzu"
date: "Füge das Datum hier hinzu"
output: 
  html_document: 
    toc: yes
    toc_float: true
---

```{r setup, include=FALSE}
# Ich habe hier ein paar Standardeinstellungen für dich vorgenommen
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Lade Packages

```{r lade-packages, message=FALSE}

library(nycflights13)  
library(dplyr)

```

# Lade Daten

```{r}

```

# Tastaturkürzel

Ich habe hier nochmals die wichtigsten Tastaturkürzel für dich hinzugefügt

- **Einen neuen Code-chunk hinzufügen:** Ctrl + Alt + I
- **Code "Zeile für Zeile" innerhalb eines Code-chunks ausführen:** Ctrl + Enter
- **Den gesamten Code-chunk ausführen:** Ctrl + Shift + Enter
- **Die Pipe (%>%):** Ctrl + Shift + M
- **Der Zuweisungs-Operator (<-)**: Alt + -

# Daten erkunden

## Daten: nycflights

Nutze die dir bekannten Funktionen um die Daten zu erkunden.

```{r}

```

## Daten: lernende





# Übungen

## Übung 4 - dplyr::mutate() 

### Notizen / Fragen - Kapitel 5.5

### Kapitel - 5.5.2 Exercises

1. Currently `dep_time` and `sched_dep_time` are convenient to look at, but hard to compute with because they're not really continuous numbers.
  Convert them to a more convenient representation of number of minutes since midnight.
  
2. Compare `air_time` with `arr_time - dep_time`.
   What do you expect to see?
   What do you see?
   What do you need to do to fix it?

3. Compare `dep_time`, `sched_dep_time`, and `dep_delay`.
   How would you expect those three numbers to be related?

4. Find the 10 most delayed flights using a ranking function.
   How do you want to handle ties?
   Carefully read the documentation for `min_rank()`.

5. What does `1:3 + 1:10` return?
   Why?